---
title: "Avian Keratin Disorder"
output: html_notebook
author: Mohsen Nikfar
---

Name of the dataset CSV file: blackCappedChickadee_poecivirus_swabFecalBlood_southcentralAlaska_zylberberg_2001_2017.csv

1.  In the R chunk below, read the data file into a new dataframe, display the first 5 rows of the resulting dataframe, and use the str() function to display the dataframe structure.

```{r}

```


2.  In the R chunk below, compute (and show) the a) minimum; b) mean; c) std. dev.; and d) maximum of the nares-to-tip measure (over the entire dataset).

```{r}

```


3.  In the R chunk below, create a new data frame that consists of birds that do not have the AKD disorder (Shown by "no" under the akd column) and the virus is detected in their cloacal swab sample (Shown by "yes" under the cloacal_swab_poecivirus_detected column). Make sure that the data frame includes only location, nares to tip, and year; and display the first 5 rows of this data frame.(In other words, we want to see if there is a detection of the virus in the cloacal swab sample of healthy birds (If the answer is yes when and where we had this observations and how big were those birds))

```{r}

```


4.  In the R chunk below, create a new data frame that consists of the Eagle River records (i.e., do a row slice where location == 'Eagle River'), and display it in view spreadsheet like grid (Hint: use fix function). Plot the nares to tip measure for the Eagle River data frame using a simple plot() function.

```{r}

```


5.  In the R chunk below, define a mask for the observations in April (January is shown by 1 then what month number is April?) and another for the birds that a buccal swab sample is taken from them (In the buccal_swab_poecivirus_detected column is not mentioned "not tested". yes or no values are acceptable). Then use this mask to create a data frame for the observations in April that a buccal swab sample is taken from birds. How many buccal swab sample is taken from birds in April?

```{r}

```


