---
title: "Some Initial Dataframe Experimentation With Our Tips Dataset"
output: html_notebook
author: Jeff Smith
---

Name of the dataset CSV file: 12_meals.csv

1.  In the R chunk below, read the data file into a new dataframe, display the first 5 rows of the resulting dataframe, and use the str() function to display the structure.
```{r}

```


2.  In the R chunck below, create a new data frame that consists of the lunch records (i.e., do a row slice where meal == 'lunch'), and display the first 5 rows of this new data frame.

```{r}

```


3.  In the R chunck below, compute (and show) the a) total; b) mean; and c) std. dev. of the tips (over the entire dataset).
```{r}

```


4.  In the R chunck below, create a new data frame that consists of snack records that were paid for by females and include only columns cost, party_size, and tip; and display the first 5 rows of this data frame.
```{r}

```


5.  In the space below, briefly describe how you verifed that your previous data frame only inlcuded the records that were specified (i.e. female/snack) given that the filter columns are not included in the dataset.  In other words, how did you verify your work?



