---
title: "Online Shoppers"
output: html_notebook
author: Jingwei Liu
---

data CSV file: online_shoppers.csv

Q1. In the R chunk below, read the data file into a dataframe, display the first 5 rows of the resulting dataframe, and use the str() function to display the dataframe structure. 

```{r}

```

Q2. In the R chunk below, compute and show (use sprintf) the a) maximum; b) mean; c) std. dev.; and d) minimum; e) median of the attribute [ExitRates].

```{r}

```

Q3. In the R chunk below, a) create a new dataframe that only contains 2 attribute columns [OperatingSystems, Browser] in region 1 to 3; b) use the new dataframe calculate how many shoppers in region 1 use [OperatingSystems] equals to 1 and [Browser] equals to 2.

```{r}

```

Q4.In the R chunk below, a) define a mask that the attribute column [Month] is "Nov" and the attribute column [ProductRelated] is greater than 3 (>3). Then, use this mask to create a new dataframe which only contains 3 attribute columns [VisitorType, Weekend, Revenue]; b) display the first 5 rows of this new dataframe. 

```{r}

```

Q5. In the R chunk below, use the dataframe created in Q4, a) calculate how many shoppers buy products in Nov; b) how many "New_Vistor" in Nov; c) how many "Returning_Vistor" buy products at weekend in Nov.

```{r}

```

